PROTEST

### 2019-09-11 article/main.tex
article: adding saplings

    Plots whose composition was not among the 7 expected compositions were dropped at this stage.

@@

    \item Thereafter, we retrieved the list of compositions observed of the PROTEST plots within each vegetation type (i.e. TFV type). This list could contain repetitions (because the same composition could be observed several times within a single TFV type). However, because 5 TFV types represented more than 96\% of the forest area and because the remaining 3\% belonged to 15 different TFV types, we previously grouped some TFV types together. The 15 under-represented TFV types have either been removed or integrated into one of the 5 main TFV types (see SI).

    \item Finally, to assign a composition to a forest plot located in a specific TFV type, we randomly selected a composition from the list of compositions associated to this TFV type while complying with the composition type allready assigned to the plot (i.e. deciduous, coniferous or deciduous-coniferous mixture). Thus plots classified as deciduous could be assigned 2 compositions: beech or oak; plots classified as coniferous could be assigned 3 compositions: fir, spruce or fir-spruce mixture; and plots classified as deciduous-coniferous mixture could be assigned 2 compositions: beech-fir or beech-spruce.

@@

  \noindent where $\alpha$ and $\beta_{1-X}$ are parameters to estmiate and $\varepsilon$, the model residuals. We applied the same variable selection procedure as the one we applied to the site index model (see final model in SI). Here, we used $G_{fir}$ and $G_{spruce}$ obtained from "true fir-spruce mixtures" and after having assigned the basal area of non-target species to the target species (see the \textit{composition initialisation} section). "True mixtures" were PROTEST plots where the two mixed species represented more than 75\% of the total basal area before the grouping of species.

@@

  where $Dg_i$ and $Dg_j$ are the quadratic diameters of species $i$ and $j$; $\alpha$ and $\beta_{1-X}$, parameters to estmiate; and $\varepsilon$, the model residuals. Here, we used $Dg_i$ and $Dg_j$ obtained from "true mixtures", i.e. PROTEST plots where the two mixed species represented more than 75\% of the total basal area, and this, before the grouping of species. We applied the same variable selection procedure as the one we applied to the site index model (see the three mixture-specific final models in SI).

>>>>

    Here, saplings were taken into account. Viable deciduous saplings and coppice sprigs were considered as unidentified deciduous. Their basal area could therefore be assigned to oak and/or beech afterwards. Viable coniferous saplings were considered as unidentified coniferous. Their basal area could therefore be assigned to fir and/or spruce afterwards. Since we had no information on the identity of the non-viable saplings, we assigned their basal area to deciduous and coniferous saplings depending on the relative proportion of these two categories. Plots whose composition was not among the 7 expected compositions were dropped at this stage.

@@

    \item Thereafter, we retrieved the list of compositions of the PROTEST plots within each vegetation type (i.e. TFV type). This list could contain repetitions (because the same composition could be observed several times within a single TFV type). However, because 5 TFV types represented more than 96\% of the forest area and because the remaining 3\% belonged to 15 different TFV types, we previously grouped some TFV types together. The 15 under-represented TFV types have either been removed or integrated into one of the 5 main TFV types (see SI).

    \item Finally, to assign a composition to a forest plot located in a specific TFV type, we randomly selected a composition from the list of compositions associated to this TFV type. We made sure that the selected composition was in line with the composition type allready assigned to the plot (i.e. deciduous, coniferous or deciduous-coniferous mixture). Another composition was randomly selected until this condition was met.

@@

  \noindent where $\alpha$ and $\beta_{1-X}$ are parameters to estmiate and $\varepsilon$, the model residuals. We applied the same variable selection procedure as the one we applied to the site index model (see final model in SI). Here, we worked with "true fir-spruce mixtures": PROTEST plots where fir and spruce represented more than 75\% of the total basal area of trees (saplings were not taken into account since we do not know their identity). We then assigned the basal area of non-target species (including the saplings basal area) to $G_{fir}$ and $G_{spruce}$ depending on the relative proportion of fir and spruce.

@@

  where $Dg_i$ and $Dg_j$ are the quadratic diameters of species $i$ and $j$; $\alpha$ and $\beta_{1-X}$, parameters to estmiate; and $\varepsilon$, the model residuals. We applied the same variable selection procedure as the one we applied to the site index model (see the three mixture-specific final models in SI). Here, we used $Dg_i$ and $Dg_j$ obtained from "true mixtures", i.e. PROTEST plots where the two mixed species represented more than 75\% of the total basal area of trees (saplings were not taken into account since we do not know their identity).
